```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
library(ggplot2)
theme_set(theme_bw(base_size=12))
library(dplyr)
```
##Homework 3
*Enter your name and EID here*

**This homework is due on Feb. 9, 2016 at 11:59pm. Please submit as a PDF file on Canvas.**

In this homework, you are asked to evaluate two data sets and determine if they are tidy data sets. *We are referring to a very specific definition of "tidy", so if this term is unfamiliar to you, please review the lecture materials*.

**Question 1: (4 pts)** *The dataset `VADeaths` built into R lists death rates per 1000 people in Virginia in 1940. You can run `?VADeaths` to learn more about this data set.*
```{r}
VADeaths
```
*Using the formal definition of tidy data that we learned in lecture, is this data set tidy? Explain why or why not.*

Your answer goes here. 2-3 sentences only.

*The data set `InsectSprays` built into R contains counts of insects (in agricultural units) after treatment with different types of insecticides. You should be familiar with this data set from Homework 1. You can run `?InsectSprays` to learn more about this data set.*
```{r}
head(InsectSprays)
```
*Using the formal definition of tidy data that we learned in lecture, is this data set tidy? Explain why or why not.*
 
Your answer goes here. 2-3 sentences only.
 
**Question 2: (2 pts)** *The `gapminder` dataset from the "gapminder" package contains information about life expectancy, GDP per capita, and population by country from 1952 to 2007. **NOTE:** You will have to install the 'gapminder' package using the command `install.packages("gapminder")` before you can load the `gapminder` dataset.*

```{r}
library(gapminder)
head(gapminder)
```

*Pick a continent and a year of your choosing. What is the **median** life expectancy for people living on that continent in the year that you chose? State your answer in a sentence. **NOTE:** The `gapminder` data set contains life expectancy data in 5 year increments beginning in 1952. Also, do not worry about the fact that you are computing a median of medians and not the true median life expectancy for the whole continent.*

State which continent and year you chose here.

```{r}
# R code goes here
```

Your answer goes here. 1 sentence only.

**Question 3: (4 pts)** *Which countries have the largest difference between the highest and lowest reported life expectancies between **1988 and 2007**? List at least the top 5 and state your answer in a sentence. **HINT:** Use the functions `max()` and `min()` to determine the difference in life expectancy.*

```{r}
# R code goes here
```

Your answer goes here. 1 sentence only.

*Choose a country from your list above and create a line plot of the life expectancy over time between **1952 and 2007**.*

State which country you chose here.

```{r}
# R code goes here
```
