```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
library(ggplot2)
theme_set(theme_bw(base_size=12))
library(dplyr)
library(tidyr)
```
##Homework 4
*Enter your name and EID here*

**This homework is due on Feb. 16, 2016 at 11:59pm. Please submit as a PDF file on Canvas.**

**Question 1: (4 pts)** *Recall the `HairEyeColor` data set from an earlier in-class exercise. This data set contains counts of males and females with different combinations of hair and eye color.*

```{r}
HairEyeColor
```

*I have split the data set into two data-frames, one `male` and one `female`. Using the `dplyr` and `tidyr` packages, make these data-frames tidy and then combine them into a single data-frame. Make sure that your final data-frame has a `sex` column indicating which data-frame the observations originally came from. **HINT**: You can use the `bind_rows` function to add rows from one data-frame onto another as long as both data-frames have identical column names.* 

```{r}
male <- read.table(text="
Hair    Brown Blue Hazel Green
  Black    32   11    10     3
  Brown    53   50    25    15
  Red      10   10     7     7
  Blond     3   30     5     8
", head=T)

female <- read.table(text="
Hair    Brown Blue Hazel Green
  Black    36    9     5     2
  Brown    66   34    29    14
  Red      16    7     7     7
  Blond     4   64     5     8
", head=T)

# R code goes here.

```

*Using the data-frame you created above, compute the total counts for each sex (i.e., the sum of the counts for each sex).*

```{r}

# R code goes here.

```

**Question 2: (3 pts)** *Recall that the `InsectSprays` data-set contains information about the effectiveness of different insecticides. The different insecticides are labeled A through F in the `spray` column. I have created a new data-frame (`spray_names`), that contains the full names of each insecticide. Using one of the `dplyr` join functions, combine the two data-frames so that there is an additional `full_name` column and all of the original columns and rows in `InsectSprays` are retained. Which join function is most appropriate to use and why?*

```{r}
head(InsectSprays)

spray_names <- read.table(text="
spray full_name
A Brigade
B Dimilin
C Movento
D Synapse
E Timectin
F Tombstone
", head=T)

# R code goes here.

```

Discussion goes here. 1-2 sentences.

**Question 3: (3 pts)** *Make up your own data set which is **not** tidy. First, explain why it is not tidy. Then, using `dplyr` and/or `tidyr`, convert it into a tidy data set.*

```{r}

# Your data set goes here.

```

Explain why your data set is not tidy here. 2-3 sentences.

```{r}

# R code to make your data set tidy goes here.

```
