```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=4, fig.width=6)
library(ggplot2)
theme_set(theme_bw(base_size=12))
library(dplyr)
```
##Homework 5
*Enter your name and EID here*

**This homework is due on Mar. 1, 2016 at 11:59pm. Please submit as a PDF file on Canvas.**

*For this homework you will use the `wine` data set. The `wine` data set contains concentrations of 13 different chemical compounds (`chem1`-`chem13`) in 178 samples of wines grown in Italy. Each row is a different sample of wine, and the data set contains three different cultivars (`cultivar`) of wine.*

```{r}
wine <- read.csv("http://wilkelab.org/classes/SDS348/data_sets/wine.csv", colClasses = c("cultivar" = "factor"))
head(wine)
```

**Question 1 (3 pts):** *Perform a principal components analysis (PCA). Since the chemical concentrations may span several orders of magnitude across different compounds, be sure to **scale** the data (using `scale`) before doing PCA. Create a scatterplot of PC1 vs. PC2 and color each point by cultivar. What do you observe? Visually, and without doing any calculations, do the cultivars cluster together in principal-component space?*

```{r}

# R code goes here.

```

*Discussion goes here. 1-2 sentences.*

**Question 2 (4 pts):** *Now take your matrix of **principal components coordinates** (not the raw chemical concentration data!) from Question 1 above and cluster the wines into 3 groups (`centers=3`) using k-means clustering with 10 random starts (`nstart=10`). Create a scatterplot of PC1 vs. PC2. This time, color each point by **cluster** and set the plotting symbol by **cultivar**. What do you observe?*

```{r}

# R code goes here.

```

*Discussion goes here. 1-2 sentences.*

**Question 3 (3 pts):** *Create a bar plot that shows the percent variance explained by each principal component. State how much variance is explained by each of the principal components 1 through 4.*

```{r}

# R code goes here

```

*Discussion goes here. 1-2 sentences.*