```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
library(ggplot2)
theme_set(theme_bw(base_size=12))
```
##Homework 2
*Enter your name and EID here*

**This homework is due on Feb 3, 2015 in class.**

**Question 1: (3 pts)** *We will be working with the `msleep` data set that is provided with ggplot2. The data set contains information about the sleep habits of 83 mammals. Enter `?msleep` on the R command line to learn more about the dataset.*

*Make the following plots: (i) a plot of total time awake vs. body weight, colored by "vore" (carnivore, herbivore, etc.); (ii) a plot of body weight vs. brain weight, colored by "vore". When you plot body weight and/or brain weight, consider whether a linear scale or a logarithmic scale seems more appropriate, and explain your reasoning in 1-2 sentences.*
```{r}
# R code goes here.
```
Discussion goes here.

**Question 2: (3 pts)** *We continue working with the `msleep` dataset. Now plot the distribution of awake times for the different species, separated by "vore". Use `geom_density()` and make sure you set the `fill` aesthetic. Make two plots: (i) one in which all distributions are plotted on top of each other, semi-transparently; (ii) one in which you facet by "vore". Explain the benefits and draw-backs of the two graphs in 1-2 sentences.*

```{r}
# R code goes here.
```
Discussion goes here.

**Question 3: (4 pts)** *Explain the difference between `geom_line()` and `geom_path()`. Make up a simple data set (5-10 data points), plot it twice, once using `geom_line()` and once using `geom_path()`, and explain why each plot looks the way it does.*

Discussion goes here.
```{r}
# R code goes here.
```



