```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
library(ggplot2)
theme_set(theme_bw(base_size=12))
library(MASS)
library(dplyr)
```
##Homework 3
*Enter your name and EID here*

**This homework is due on Feb 10, 2015 in class.**

**Question 1: (4 pts)** *The datset `AirPassengers` built into R lists total numbers of international airline passengers, 1949 to 1960.*
```{r}
AirPassengers
```
*Is the dataset tidy? Explain why or why not.*

Explanation goes here.

*The datset `HairEyeColor` built into R contains the distribution of hair color, eye color, and sex in 592 statistics students.*
```{r}
HairEyeColor
```
*Is the dataset tidy? Explain why or why not.*
 
Explanation goes here.

**Question 2: (2 pts)** *The function `data()` lists all datasets that are available in R by default. Look through the list and identify a dataset that is tidy. Explain why the dataset is tidy.*

I pick the dataset: ...
```{r}
# Display the first few rows of your chosen dataset:
# head()
```
Explanation goes here.

**Question 3: (2 pts)** *The package nycflights13 contains information about all flights departing from one of the NY City airports in 2013. In particular, the data table `flights` lists on-time departure and arrival information for 336,776 individual flights:*
```{r}
library(nycflights13)
flights
```

*We would like to collect some information about arrival delays of United Airlines (UA) flights. Do the following: pick all UA departures with non-zero arrival delay, calculate the mean arrival delay for each of the corresponding flight numbers, and find the five flights with the largest mean delay.*

```{r}
# R code goes here.
```
Summary of finding goes here.

**Question 4: (2 pts)** *In an in-class exercise, we made the following plot of the Sitka dataset:*

```{r}
ggplot(Sitka, aes(x=Time, y=size, group=tree)) + geom_line() + facet_wrap(~treat)
```

*Now modify the plot so that the line for each tree is colored according to the maximum size of the tree.* 
```{r}
# R code goes here.
```
