```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
library(ggplot2)
theme_set(theme_bw(base_size=12))
library(tidyr)
library(dplyr)
```
##Homework 4
*Enter your name and EID here*

**This homework is due on Feb 17, 2015 in class.**


**Question 1: (2 pts)** *For the `msleep` data set from ggplot2, calculate how many distinct orders there are within each "vore". Hint: use the functions `distinct()` and `tally()`.*

```{r}
# R code goes here.
```

 
**Question 2: (4 pts)** *Invent two simple data sets that allow you explain the difference between the dplyr functions `left_join()` and `inner_join()`. Explain which features of your data sets affect the behavior of these two functions.*
```{r}
# R code goes here.
```
Explanation goes here.

**Question 3: (2 pts)** *The following code downloads a data set containing information about total international air passengers from 1950 to 1961:*
```{r}
air <- read.csv("http://wilkelab.org/classes/SDS348/data_sets/AirPassengers.csv")
air
```
*Convert this data set into a table with three columns, one for the year, one for the month, and one for the number of passengers.*
```{r}
# R code goes here.
```


**Question 4: (2 pts)** *The `sleep` dataset contains amount of extra sleep (in hours) for ten students treated with two different drugs each. The drug treatment is indicated in the `group` column:*
```{r}
head(sleep)
```

*Convert this table into a wide table that has three columns, one for student ID, one for extra sleep under treatment 1, and one for extra sleep under treatment 2.* 
```{r}
# R code goes here.
```
