```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=4, fig.width=5)
library(ggplot2)
theme_set(theme_bw(base_size=12))
library(dplyr)
library(tidyr)
library(grid)
```
## Project 2 
*Enter your name and EID here*

###Instructions
Please submit both this completed Rmarkdown document and its knitted HTML, converted to PDF, on Canvas **no later than 11:59 pm on March 29th, 2016**. These two documents will be graded jointly, so they must be consistent (as in, don't change the Rmarkdown file without also updating the knitted HTML!).

All results presented **must** have corresponding code. Any answers/results given without the corresponding R code that generated the result will be considered absent. All code reported in your final project document should work properly. Please bear in mind that **you will lose points** for the following:

+ an R-code chunk with no comments
+ results without corresponding R code
+ extraneous code which does not contribute to the question

For this project, you will work with a dataset collected from Pima Native American women. Studies have shown that Pima women have a much higher incidence of Type II Diabetes than the general population. Since the 1960s, NIH researchers have periodically asked Pima women to undergo various medical tests in order to assess possible diabetes risk factors. Consequently, data on Pima women has proven useful for predicting how likely an individual is to develop diabetes. [Source: J. W. Smith, J. E. Everhart, W. C. Dickson, W. C. Knowler, and R. S. Johannes (1988). Using the ADAP learning algorithm to forecast the onset of diabetes mellitus. In Symposium on Computer Applications in Medical Care, 261–265.]
Your goal for this project is to analyze the Pima women dataset using several statistical approaches we have learned, in two parts.

We have already subdivided the full data set into training and test data sets (`pima_training` and `pima_test`). And we also provide the full data set (`pima_full`). Please use the training and test data sets for Part 1 and either data set for Part 2. 


```{r}
##### Use these datasets for part 1 (described below) #####
# Dataset to use specifically for training in Part 1
pima_training <- read.csv("http://wilkelab.org/classes/SDS348/2016_spring/projects/project2/pima_training.csv")
# Dataset to use specifically for testing your model in Part 1
pima_test <- read.csv("http://wilkelab.org/classes/SDS348/2016_spring/projects/project2/pima_test.csv")

##### Use this dataset for part 2 (described below) #####
# Complete Pima data, with a single observation per individual
pima_full <- read.csv("http://wilkelab.org/classes/SDS348/2016_spring/projects/project2/pima.csv")

head(pima_full)
```
The column contents are as follows:

+ **npreg**: number of times pregnant
+ **glucose**: plasma glucose concentration at 2 hours in an oral glucose tolerance test (units: mg/dL)
+ **dpb**: diastolic blood pressure (units: mm Hg)
+ **skin**: triceps skin-fold thickness (units: mm)
+ **insulin**: 2-hour serum insulin level (units: $\mu$U/mL)
+ **bmi**: Body Mass Index
+ **age**: age in years
+ **diabetic**: whether or not the individual has diabetes

**Part 1 (40 points)**. We have divided the dataset, which consists of observations from 768 individuals, into a training and a test data set. Fit a logistic regression model (to predict diabetes incidence) on the training data set. When building your model, use backwards selection to choose predictors which are significant **at your chosen significance level (be sure to report your chosen value!)**. Your code should be appropriately commented with high-level statements about the code's function.

Using your final model, predict the outcome on the test data set, and plot and discuss your results. You should have two final plots: a plot with two ROC curves for the training and test data each, and a plot of the fitted probability of diabetes incidence as a function of the predictors, colored by diabetes, on the test data. Your discussion should, at least, cover the differences and similarities in model performance on the training vs. test data (including AUC) as well as a clear interpretation of each plot. Please limit your discussion to a maximum of 8 sentences.


**Part 2 (60 points)**. Think of two **scientific** questions to ask about this data set (for this, you are welcome to use either the training, test, or full data set). Scientific questions should not be procedural, they should be **conceptual**. (For example, "What is the distribution of ages?" is a **procedural** question because all it asks you to do is plot a distribution, but, "Are incidence of diabetes higher in older women or in younger women?" is a **conceptual** question because you have to determine which type of plot is appropriate for the question and interperet that plot.) For each question, perform an exploratory statistical analysis (PCA, k-means, logistic regression, linear model, etc.) with a corresponding figure. Discuss your findings, in particular how your analysis' results reveal (or don't reveal) an answer your proposed question. Please limit each question's discussion to a maximum of 5 sentences.

Project responses should be entered below.

***  

```{r}
# This R code chunk contains the calc_ROC function.
calc_ROC <- function(probabilities, known_truth, model.name=NULL)
  {
  outcome <- as.numeric(factor(known_truth))-1
  pos <- sum(outcome) # total known positives
  neg <- sum(1-outcome) # total known negatives
  pos_probs <- outcome*probabilities # probabilities for known positives
  neg_probs <- (1-outcome)*probabilities # probabilities for known negatives
  true_pos <- sapply(probabilities,
                     function(x) sum(pos_probs>=x)/pos) # true pos. rate
  false_pos <- sapply(probabilities,
                     function(x) sum(neg_probs>=x)/neg)
  if (is.null(model.name))
    result <- data.frame(true_pos, false_pos)
  else
    result <- data.frame(true_pos, false_pos, model.name)
  result %>% arrange(false_pos, true_pos)
  }
```


**Part 1**
```{r}
# R code for part 1 goes here.
```
*Discussion for part 1 goes here.*    

<br><br><br>

**Part 2**

*Question 1 goes here.*
```{r}
# R code for question 1 goes here
```
*Discussion for question 1 goes here.*


<br> 

*Question 2 goes here.*
```{r}
# R code for question 2 goes here
```
*Discussion for question 2 goes here.*


