```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
library(ggplot2)
theme_set(theme_bw(base_size=12))
library(dplyr)
```
##Lab Worksheet 3

**Question 1:** *The data set `AirPassengers` built into R lists total numbers of international airline passengers, 1949 to 1960.*
```{r}
AirPassengers
```
*Is the dataset tidy? Explain why or why not.*

Your answer goes here.

**Question 2:** *The function `data()` lists all data sets that are available in R by default. Look through the list and identify a data set that is tidy. Explain why the data set is tidy.*

I pick the data set... :
```{r}
# R code goes here
```
Your answer goes here.

**Question 3:** *In an in-class exercise, we made the following plot of the Sitka dataset:*

```{r}
# download the sitka data set:
sitka <- read.csv("http://wilkelab.org/classes/SDS348/data_sets/sitka.csv")
head(sitka)
ggplot(sitka, aes(x=Time, y=size, group=tree)) + geom_line() + facet_wrap(~treat)
```

*Now modify the plot so that the line for each tree is colored according to the maximum size of the tree.* 
```{r}
# R code goes here
```

### If that was easy...

**Question 4:** *The package nycflights13 contains information about all flights departing from one of the NY City airports in 2013. In particular, the data table `flights` lists on-time departure and arrival information for 336,776 individual flights:*
```{r}
library(nycflights13)
flights
```

*We would like to collect some information about arrival delays of United Airlines (UA) flights. Do the following: pick all UA departures with non-zero arrival delay and calculate the mean arrival delay for each of the corresponding flight numbers. Which flight had the longest mean arrival delay and how long was that delay?*

```{r}
# R code goes here.
```

Your answer goes here.

