```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
library(ggplot2)
theme_set(theme_bw(base_size=12))
library(tidyr)
library(dplyr)
```
##Lab Worksheet 4

### Part 1: The dplyr pipe

The following questions in Part 1 are from Lab Worksheet 3. Answer these questions again, but this time use the dplyr pipe (`%>%`) in your answer.

**Question 1:** *In an in-class exercise, we made the following plot of the Sitka dataset:*

```{r}
# download the sitka data set:
sitka <- read.csv("http://wilkelab.org/classes/SDS348/data_sets/sitka.csv")
head(sitka)
ggplot(sitka, aes(x=Time, y=size, group=tree)) + geom_line() + facet_wrap(~treat)
```

*Now modify the plot so that the line for each tree is colored according to the maximum size of the tree.* 
```{r}
# R code goes here.
```

**Question 2:** *The package nycflights13 contains information about all flights departing from one of the NY City airports in 2013. In particular, the data table `flights` lists on-time departure and arrival information for 336,776 individual flights:*
```{r}
library(nycflights13)
flights
```

*We would like to collect some information about arrival delays of United Airlines (UA) flights. Do the following: pick all UA departures with non-zero arrival delay and calculate the mean arrival delay for each of the corresponding flight numbers. Which flight had the longest mean arrival delay and how long was that delay?*

```{r}
# R code goes here.
```

Discussion goes here. 1-2 sentences.

###Part 2: Combining data-frames with dplyr

**Question 1:** *Invent two simple data sets that allow you explain the difference between the dplyr functions `left_join()` and `inner_join()`. Explain which features of your data sets affect the behavior of these two functions.*
```{r}
# R code goes here.
```
Discussion goes here. 3-4 sentences.

**Question 2:** *I have split the sitka data set into two data-frames. First, look up the documentation for the `bind_rows` function. What does `bind_rows` do? Next, use `bind_rows` to combine `sitka1` and `sitka2` back into a single data-frame.*

Discussion goes here. 1-2 sentences.

```{r}
sitka1 <- sitka[1:100,]
sitka2 <- sitka[101:395,]
head(sitka1)
head(sitka2)

# R code goes here.
```