```{r global_options, include=FALSE}
library(knitr)
library(ggplot2)
opts_chunk$set(fig.align = "center", fig.height = 4, fig.width = 6)
```
## Homework 2
*Enter your name and EID here*

**This homework is due on Feb. 5, 2019 at 4:00pm. Please submit as a PDF file on Canvas.**

This homework uses the `Cars93` data set. Each observation in the data frame contains information on passenger cars from 1993. This is a big data frame with 27 columns. We are interested in the information on manufacturer (`Manufacturer`), car model (`Model`), type of car (`Type`), car company origin (`Origin`), midrange price in $1000 (`Price`), city MPG (miles per US gallon, `MPG.city`), and fuel tank capacity in gallons (`Fuel.tank.capacity`). 

```{r}
Cars93 <- read.csv("http://wilkelab.org/classes/SDS348/data_sets/Cars93.csv")
head(Cars93)
```

**Problem 1: (2 pts)** Use ggplot2 to create a scatter plot of the city MPG versus the car prices. In the same plot, fit a curve to these data using `geom_smooth()`. In one sentence, what broad trend do you observe in city MPG for different car prices? **HINT**: Plot city MPG on the y-axis and price on the x-axis.

```{r}
ggplot(Cars93, aes(x = Price, y = MPG.city)) + geom_point() + geom_smooth()
```

City MPG decreases with price until $20,000, and it levels off after.

**Problem 2: (4 pts)** Next, create a bar plot that shows the origin of cars, stacked on top of each other, for each car type. Make two observations about the data from this plot. State each in 1 sentence.

```{r}
ggplot(Cars93, aes(x = Type, fill = Origin)) + geom_bar()
```

Observations:

1. Large cars are only produced by the US companies.

2. For each car type, there are roughly equal amounts of cars of each origin.

3. Most of the cars in this dataset are midsize or small.

**Problem 3: (2 pts)** Plot the distribution of fuel tank capacity, once using `geom_histogram()` and once using `geom_density()`. 

```{r}
ggplot(Cars93, aes(x = Fuel.tank.capacity)) + geom_histogram()
ggplot(Cars93, aes(x = Fuel.tank.capacity)) + geom_density()
```

**Problem 4: (2 pts)** What does the y-axis in your histogram represent? In your density plot, what is the *total* area under the curve? For the total area, please give a single number as your answer. **HINT**: You do not need to do any additional calculations to determine the area under the curve. Use Google to find the answer. 

The y-axis in a histogram represents counts in a given range of x-values (bins). The area under the curve of a density plot always sums to 1.
