```{r global_options, include=FALSE}
library(knitr)
library(ggplot2)
opts_chunk$set(fig.align="center", fig.height=4, fig.width=6)
```
## Homework 2
*Enter your name and EID here*

**This homework is due on Feb. 5, 2019 at 4:00pm. Please submit as a PDF file on Canvas.**

This homework uses the `Cars93` data set. Each observation in the data frame contains information on passenger cars from 1993. This is a big data frame with 27 columns. We are interested in the information on manufacturer (`Manufacturer`), car model (`Model`), type of car (`Type`), car company origin (`Origin`), midrange price in $1000 (`Price`), city MPG (miles per US gallon, `MPG.city`), and fuel tank capacity in gallons (`Fuel.tank.capacity`). 

```{r}
Cars93 <- read.csv("http://wilkelab.org/classes/SDS348/data_sets/Cars93.csv")
head(Cars93)
```

**Problem 1: (2 pts)** Use ggplot2 to create a scatter plot of the city MPG versus the car prices. In the same plot, fit a curve to these data using `geom_smooth()`. In one sentence, what broad trend do you observe in city MPG for different car prices? **HINT**: Plot city MPG on the y-axis and price on the x-axis.

```{r}
# R code goes here
```

Your answer goes here. 1 sentence only.

**Problem 2: (4 pts)** Next, create a bar plot that shows the origin of cars, stacked on top of each other, for each car type. Make two observations about the data from this plot. State each in 1 sentence.

```{r}
# R code goes here
```

Your answer goes here. 2 sentences only.

**Problem 3: (2 pts)** Plot the distribution of fuel tank capacity, once using `geom_histogram()` and once using `geom_density()`. 

```{r}
# R code goes here
```

**Problem 4: (2 pts)** What does the y-axis in your histogram represent? In your density plot, what is the *total* area under the curve? For the total area, please give a single number as your answer. **HINT**: You do not need to do any additional calculations to determine the area under the curve. Use Google to find the answer. 

Your answer goes here. 2-3 sentences only.