```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
library(ggplot2)
theme_set(theme_bw(base_size=12))
library(dplyr)
```
## Homework 3
*Enter your name and EID here*

**This homework is due on Feb. 12, 2019 at 4:00pm. Please submit as a PDF file on Canvas.**

In this homework, you are asked to evaluate two data sets and determine if they are tidy data sets. *We are referring to a very specific definition of "tidy", so if this term is unfamiliar to you, please review the lecture materials*.

**Problem 1: (2 pts)** The dataset `USAccDeaths` built into R contains accidental deaths in the US 1973-1978. You can run `?USAccDeaths` to learn more about this data set.
```{r}
USAccDeaths
```
Explain the variables present in this dataset. Using the variables in this dataset and the formal definition of tidy data that we learned in lecture, is this data set tidy? Explain why or why not.

*The dataset contains the variables for year, month, and number of accidental deaths. The dataset is not tidy. There should be one column for year, one column for month, and one column for number of accidental deaths. Instead, the data are arranged such that months vary along the columns and years vary along the rows. Accidental death count varies along both the rows and the columns.*

The dataset `CO2` built into R contains data on the carbon dioxide uptake in grass plants. You can run `?CO2` to learn more about this data set.
```{r}
head(CO2)
```
Explain the variables present in this dataset. Using the variables in this dataset and the formal definition of tidy data that we learned in lecture, is this data set tidy? Explain why or why not.

*The dataset contains the variables for plant, plant origin, treatment, concentration of CO2, and CO2 uptake rate. The dataset is tidy because each column is a variable, and each row is an observation.*

**Problem 2: (5 pts)** Listed below are three examples of code that violate the rules in [section 2](https://style.tidyverse.org/syntax.html) of the tidyverse style guide. Which tidyverse style guidelines are violated in these examples?
```{r, eval = FALSE}
iris %>% filter(Species=="versicolor") %>% head()
```

*The spaces on both sides of `==` are missing and the pipes are written on one line*

```{r, eval = FALSE}
iris[50,]
```

*There is no space after the comma*

```{r, eval = FALSE}
boxplot (len ~ dose, data = ToothGrowth, range = 1, width = c(2, 2, 2), varwidth = TRUE, notch = FALSE, outline = TRUE)
```

*There is a space before `(` and the line is too long to fit on a single line*

**Problem 3: (3 pts)** The `NCbirths` contains 1409 birth records from North Carolina in 2001. The column contents are as follows:

+ **Plural**: 1=single birth, 2=twins, 3=triplets.
+ **Sex**: Sex of the baby 1=male 2=female.
+ **MomAge**: Mother's age (in years).
+ **Weeks**: Completed weeks of gestation.
+ **Gained**: Weight gained during pregnancy (in pounds).
+ **BirthWeightGm**: Birth weight in grams.
+ **Low**: Indicator for low birth weight, 1=2500 grams or less, 0=otherwise.
+ **Premie**: Indicator for premature birth, 1=36 weeks or sooner, 0=otherwise.
+ **Marital**: Marital status: 0=married or 1=not married.

```{r}
NCbirths <- read.csv("http://wilkelab.org/classes/SDS348/data_sets/NCbirths.csv")
head(NCbirths)
```

For single births, what are the **max** completed weeks of gestation and the **mean** birth weight for babies that were born prematurely and for babies that were carried to term? State your answer in a sentence. **HINT:** Use the function `max()` to determine the maximum completed weeks of gestation.

```{r}
NCbirths %>%
  filter(Plural == 1) %>%
  group_by(Premie) %>%
  summarize(max_Weeks = max(Weeks), mean_BirthWeight = mean(BirthWeightGm))
```

*The maximum number of weeks of gestation for premature babies is 36 and for babies that were carried to term is 45. The mean birth weight for premature babies is around 2616 grams and for babies that were carried to term is around 3431 grams.*
