```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align = "center", fig.height = 3, fig.width = 4)
library(ggplot2)
theme_set(theme_bw(base_size = 12))
library(dplyr)
library(tidyr)
```
## Homework 4

*Enter your name and EID here*

**This homework is due on Feb. 19, 2019 at 4:00pm. Please submit as a PDF file on Canvas.**

**Problem 1: (4 pts)** The following two data tables contain information about how many male and female passengers traveling on the Titanic in different classes survived or died. The data-frame `survived` contains information about passengers that survived, and the data-frame `deceased` contains information about passendgers that died. Using the `dplyr` and `tidyr` packages, make these data-frames tidy and then combine them into a single data-frame. Make sure that your final data-frame has a `survival_status` column indicating which data-frame the observations originally came from. HINT: You can use the `bind_rows` function to add rows from one data-frame onto another as long as both data-frames have identical column names.

```{r}
survived <- read.table(text = "
class  male female
1st    57    140
2nd    14     80
3rd    75     76
crew  192     20
", head = T)

deceased <- read.table(text = "
class  male female
1st   118      4
2nd   154     13
3rd   387     89
crew  670      3
", head = T)

# R code goes here
```

Using the data-frame you created above, compute the total number of passengers that survived and that did not survive.

```{r}
# R code goes here
```

**Problem 2: (3 pts)** The `chickwts` dataset contains information on the weight of chicks after being fed different feed supplements. The different feed supplements are labeled casein, horsebean, linseed, meatmeal, soybean, and sunflower in the `feed` column. I have created a new data-frame (`feed_names`), that contains the abbreviated names of different feed supplements. Using one of the `dplyr` join functions, combine the two data-frames so that there is an additional `feed_abbr` column and all of the original columns and rows in chickwts are retained. Which join function is most appropriate to use and why? 

```{r}
head(chickwts)

feed_names <- read.table(text = "
feed feed_abbr
casein cs
whey wh
linseed  ls
meatmeal mm
fishmeal fm
soybean sb
sunflower sf
corn co
wheatbran wb
", head = T)

# R code goes here
```

*Your answer goes here. 1-2 sentences only.*

**Problem 3: (3 pts)** Recall the `flights` dataset from lab 3 worksheet. Ask a **conceptual** question about the `flights` dataset. Your question should not repeat the questions from class materials. Describe in 1-2 sentences how you would answer this question with an analysis or a graph.

*Your answer goes here. 2-3 sentences only.*
