```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=5, fig.width=8)
```
##Homework 1
*Enter your name and EID here*

**This homework is due on Jan. 23, 2018 at 7:00pm. Please submit as a pdf file on Canvas.**

This homework uses the `Alfalfa` data set. This data set contains the height of alfalfa sprouts after four days (`Ht4`) grown indoors in different acidic environments (`Acid`). There are three different amounts of acid observed in the data set: none (`water`), moderate (`1.5HCl`), and strong (`3.0HCl`). Each treatment was performed on 5 plants. The data set also contains information on the amount of daylight the plants received (`Row`). This column contains values `a` through `e`, where `a` indicates the row farthest from the window and `e` indicates the row closest to the window.   

```{r}
Alfalfa <- read.csv("http://wilkelab.org/classes/SDS348/data_sets/Alfalfa.csv")
head(Alfalfa)
```

**Problem 1: (4 pts)** We are interested in testing the effects of acidic environment on plant growth. Since there are three different amounts of acidity in the data set, and therefore three groups of acid measurements, we will use an analysis of variance (ANOVA) test. Conduct an ANOVA test and interpret your results in 1-2 sentences. HINT: You will first need to create a linear model object using the `lm()` function before you can use the `anova()` function.

```{r}
# R code goes here
```

*Your answer goes here. 1-2 sentences only.*

**Problem 2: (3 pts)** Create a boxplot of the plant growth, separated by acid amounts. Based on this plot, is the mean height of alfalfa grown in 3.0HCl the same or different from the mean height of alfalfa grown in water? Explain your answer.

```{r}
# R code goes here
```

*Your answer goes here. 1-2 sentences only.*

**Problem 3: (3 pts)** Use a t test to determine if the mean height of plants grown in 3.0HCl is the same or different from the mean height of plants grown in water. Interperet and explain your results in 1-2 sentences.

```{r}
# R code goes here
```

*Your answer goes here. 1-2 sentences only.*
