```{r global_options, include=FALSE}
library(knitr)
library(ggplot2)
opts_chunk$set(fig.align="center", fig.height=4, fig.width=6)
```
##Homework 2
*Enter your name and EID here*

**This homework is due on Jan. 30, 2018 at 7:00pm. Please submit as a PDF file on Canvas.**

This homework uses the `Cars93` data set. Each observation in the data frame contains information on passenger cars from 1993. This is a big data frame with 27 columns. We are interested in the information on manufacturer (`Manufacturer`), car model (`Model`), type of car (`Type`), midrange price in $1000 (`Price`), maximum horsepower (`Horsepower`), city MPG (miles per US gallon, `MPG.city`), highway MPG (`MPG.highway`), and fuel tank capacity in gallons (`Fuel.tank.capacity`). 

```{r}
Cars93 <- read.csv("http://wilkelab.org/classes/SDS348/data_sets/Cars93.csv")
head(Cars93)
```

**Problem 1: (2 pts)** Use ggplot2 to create a scatter plot of the fuel tank capacity versus the car prices. In the same plot, fit a curve to these data using `geom_smooth()`. In one sentence, what broad trend do you observe in fuel tank capacity for different car prices? **HINT**: Plot fuel tank capacity on the y-axis and price on the x-axis.

```{r}
# your R code goes here
```

*Your answer goes here. 1 sentence only.*

**Problem 2: (4 pts)** Next, create a scatter plot of city MPG against highway MPG, facetted by car type. Make two observations about the data from this plot. State each in 1 sentence.

```{r}
# your R code goes here
```

*Your answer goes here. 2 sentences only.*

**Problem 3: (2 pts)** Plot the distribution of maximum horsepower, once using `geom_histogram()` and once using `geom_density()`. 

```{r}
# your R code goes here
```

**Problem 4: (2 pts)** What does the y-axis in your histogram represent? In your density plot, what is the *total* area under the curve? Please give a single number as your answer. **HINT**: You do not need to do any additional calculations to determine the area under the curve. Use Google to find the answer. 

*Your answer goes here. 2-3 sentences only.*
