```{r global_options, include=FALSE}

library(knitr)
opts_chunk$set(fig.align = "center", fig.height = 3, fig.width = 4)
library(ggplot2)
theme_set(theme_bw(base_size = 12))
library(dplyr)

```
## Lab Worksheet 3

**Problem 1:** The data set `AirPassengers` built into R lists total numbers of international airline passengers, 1949 to 1960. Explain the variables present in this dataset. Using the variables in this dataset and the formal definition of tidy data that we learned in lecture, is this data set tidy? Explain why or why not.

```{r}

AirPassengers

```

*The dataset contains the variables for number of passengers, years, and months. The dataset is not tidy. There should be one column for year, one for month, and one for the number of passengers. Instead, the data are arranged such that years vary along the rows and months along the columns.*

**Problem 2:** The function `data()` lists all datasets that are available in R by default. Look through the list and identify a dataset that is tidy. Explain the variables present in this dataset and why the dataset is tidy.

I pick the dataset `OrchardSprays`:
```{r}

head(OrchardSprays)

```

*This dataset contains variables for row of the design (`rowpos`), column of the design (`colpos`), treatment level (`treatment`), and response (`decrease`). It contains one row per observation, one column of measured values (`decrease`), and three columns describing the conditions under which that value was measured (`rowpos`, `colpos`, `treatment`).*

**Problem 3a:** Save a tidy version of the dataset `Titanic` using the code below. Filter for those did not survive (`Survived == "No"`) and save the results in a new dataframe. What do you notice about the results?

```{r}

titanic <- as.data.frame(Titanic) # this converts the dataset `Titanic` into a tidy dataframe; doesn't always work but it will in this case

titanic_filtered <- titanic %>%
  filter(Survived == "No")

titanic_filtered

```

*More male adult passengers died than any other group of passengers.*

**Problem 3b:** Using the new dataframe you just created, group by `Class`, use `summarize()` to sum the counts, then use `mutate()` to calculate the relative percentage of deaths in a new column for each group. What can you say about these results?

```{r}

titanic_filtered %>%
  group_by(Class) %>%
  summarize(group_freq = sum(Freq)) %>% 
  mutate(percent = group_freq/sum(group_freq))

```

*Crew members and 3rd class passengers suffered the most loss, making up >80% of deaths combined.*

**Problem 4 (if time):** This package contains information about all flights that departed from NYC (e.g. EWR, JFK and LGA) to destinations in the United States, Puerto Rico, and the American Virgin Islands) in 2013: 336,776 flights in total. To help understand what causes delays, it also includes a number of other useful datasets. In particular, the data table `flights` lists on-time departure and arrival information for 336,776 individual flights:
```{r}

install.packages("nycflights13") # this dataset is not pre-installed, so you have to install it with this line of code

library(nycflights13) # and then load it with this line of code

flights

```

We would like to collect some information about arrival delays of United Airlines (UA) flights. Do the following: pick all UA departures with non-zero arrival delay and calculate the mean arrival delay for each of the corresponding flight numbers. Which flight had the longest mean arrival delay and how long was that delay?

```{r}

flights_filtered <- filter(flights, carrier == "UA" & arr_delay != 0)
flights_grouped <- group_by(flights_filtered, flight)
flights_summary <- summarize(flights_grouped, mean_delay = mean(arr_delay))
filter(flights_summary, mean_delay == max(mean_delay))

# more efficiently (and neatly, I think):
flights %>%
  filter(carrier == "UA" & arr_delay != 0) %>%
  group_by(flight) %>%
  summarize(mean_delay = mean(arr_delay)) %>%
  arrange(desc(mean_delay))

```

*Flight 1510 had the longest delay, with an average arrival delay of 283 minutes.*

