```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align = "center", fig.height = 3, fig.width = 4)
library(tidyverse)
theme_set(theme_bw(base_size = 12))
library(ggthemes)
```
## Lab Worksheet 6

In 1898, Hermon Bumpus, an American biologist working at Brown University, collected data on one of the first examples of natural selection directly observed in nature. Immediately following a bad winter storm, he collected 136 English house sparrows, *Passer domesticus*, and brought them indoors. Of these birds, 64 had died during the storm, but 72 recovered and survived. By comparing measurements of physical traits, Bumpus demonstrated physical differences between the dead and living birds. He interpreted this finding as evidence for natural selection as a result of this storm:

```{r}
bumpus <- read_csv("http://wilkelab.org/classes/SDS348/data_sets/bumpus_full.csv")
bumpus$Survival <- factor(bumpus$Survival)
head(bumpus)
```

The data set has three categorical variables (`Sex`, with levels `Male` and `Female`, `Age`, with levels `Adult` and `Young`, and `Survival`, with levels `Alive` and `Dead`) and nine numerical variables that hold various aspects of the birds' anatomy, such as wingspread, weight, etc.

**Problem 1:** Make a logistic regression model that can predict survival status from all other predictor variables. (Include the categorical predictors `Sex` and `Age`.) Then do backwards selection, removing the predictors with the highest P value one by one, until you are only left with predictors that have P<0.1. How many and which predictors remain in the final model?

```{r}
glm_out_all <- glm(Survival ~ Sex + 
                     Age + 
                     Length + 
                     Wingspread + 
                     Weight + 
                     Skull_Length + 
                     Humerus_Length + 
                     Femur_Length + 
                     Tarsus_Length + 
                     Sternum_Length + 
                     Skull_Width, 
                   data = bumpus, 
                   family = "binomial")
summary(glm_out_all)

# remove Femur_Length
glm_out <- glm(Survival ~ Sex + 
                 Age + 
                 Length + 
                 Wingspread + 
                 Weight + 
                 Skull_Length + 
                 Humerus_Length + 
                 Tarsus_Length + 
                 Sternum_Length + 
                 Skull_Width,
               data = bumpus, 
               family = "binomial")
summary(glm_out)

# remove Wingspread
glm_out <- glm(Survival ~ Sex + 
                 Age + 
                 Length + 
                 Weight + 
                 Skull_Length + 
                 Humerus_Length + 
                 Tarsus_Length + 
                 Sternum_Length + 
                 Skull_Width, 
               data = bumpus, 
               family = "binomial")
summary(glm_out)

# remove Tarsus_Length
glm_out <- glm(Survival ~ Sex + 
                 Age + 
                 Length + 
                 Weight + 
                 Skull_Length + 
                 Humerus_Length + 
                 Sternum_Length + 
                 Skull_Width, 
               data = bumpus, 
               family = "binomial")
summary(glm_out)

# remove Age
glm_out <- glm(Survival ~ Sex + 
                 Length + 
                 Weight + 
                 Skull_Length + 
                 Humerus_Length + 
                 Sternum_Length + 
                 Skull_Width, 
               data = bumpus, 
               family = "binomial")
summary(glm_out)

# remove Skull_Width
glm_out <- glm(Survival ~ Sex + 
                 Length + 
                 Weight + 
                 Skull_Length + 
                 Humerus_Length + 
                 Sternum_Length, 
               data = bumpus, 
               family = "binomial")
summary(glm_out)

# remove Skull_Length
glm_out_final <- glm(Survival ~ Sex + 
                       Length + 
                       Weight + 
                       Humerus_Length + 
                       Sternum_Length, 
                     data = bumpus, 
                     family = "binomial")
summary(glm_out_final)

head(glm_out_final$linear.predictors) # t, t = linear regression (predictor value)
head(glm_out_final$fitted.values) # y, y = probability of outcome (alive vs dead)
```
*The final model uses five predictors, `Sex`, `Length`, `Weight`, `Humerus_Length`, and `Sternum_Length`.*

**Problem 2:** Make a plot of the fitted probability as a function of the linear predictor, colored by survival. Make a density plot that shows how the two outcomes are separated by the linear predictor. Interperet your plots in 1-2 sentences. If you had to choose a cut-off value for alive or dead, where would it be?
```{r}
# combine model information with outcome
reg_data <- data.frame(
  predictor = glm_out_final$linear.predictors,
  prob = glm_out_final$fitted.values,
  Survival = bumpus$Survival
)

# plot probability curve, coloring by outcome (survival)
ggplot(reg_data, aes(x = predictor, y = prob, color = Survival)) + 
  geom_point() + 
  scale_color_colorblind()

# plot distribution of both outcomes
ggplot(reg_data, aes(x = predictor, fill = Survival)) + 
  geom_density(alpha = 0.5) + 
  scale_fill_colorblind()
```

*Our predictors do not cleanly separate the two survival outcomes alive and dead. There is no single line that can be drawn to separate survival outcomes.*

**Problem 3:** Add rugs to both the top and bottom of the plot above. **BONUS:** Add a curve for the logistic function.

```{r}
# extract data for alive and dead
alive_data <- filter(reg_data, Survival == "Alive")
dead_data <- filter(reg_data, Survival == "Dead")

# plot
ggplot(reg_data, aes(x = predictor, y = prob, color = Survival)) +
  geom_line(color = "black") +
  geom_point() +
  geom_rug(data = alive_data, sides = "b") +
  geom_rug(data = dead_data, sides = "t") +
  scale_color_colorblind()
```
