```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
library(ggplot2)
theme_set(theme_bw(base_size=12))
```
##In-class worksheet 3
**Jan 27, 2015**

## 1. Plotting the iris data set.
*Re-do question 3 from the homework with ggplot2: Make a scatter plot of petal length vs. sepal length for the three species. Then do the same plot but facet by species instead of coloring.*
```{r }
# R code goes here.
```

*Now see if you can reproduce the answer to question 2 from the homework, using ggplot2. In other words, make side-by-side boxplots of sepal lengths for the three species of iris. The geom you need to use is `geom_boxplot()`. See if you can guess the correct aesthetic mapping.*
```{r}
# R code goes here.
```

## 2. Plotting tree-growth data.
*The data set `Sitka` from the MASS package contains repeated measurements of tree size for 79 Sitka spruce trees, which were grown either in ozone-enriched chambers or under control conditions.*

```{r}
library(MASS) # we need to load the MASS library to have access to this dataset
head(Sitka)
```

*Make line plots of tree size vs. time, for each tree, faceted  by treatment. First, use the same color for all lines.*
```{r}
# R code goes here.
```

*Then, color by tree.*
```{r}
# R code goes here.
```

*Finally, color by size.*
```{r}
# R code goes here.
```


## 3. If this was easy

*Show the 2d distribution of petal length vs. sepal length in the `iris` dataset, by making an x-y plot that shows the individual data points as well as contour lines indicating the density of points in a given spatial region.*
```{r}
# R code goes here.
```

*If this was still easy, now instead of contour lines add a fitted straight black line (not a curve, and no confidence band!) to each group of points.*
```{r}
# R code goes here.
```
