```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
library(ggplot2)
theme_set(theme_bw(base_size=12))
library(dplyr)
library(grid) # required for `arrow()`
```
##In-class worksheet 10
**Feb 19, 2015**


# 1. k-means clustering of the iris data set

We can do k-means clustering in R using the function `kmeans()`. The primary argument to this function is `centers`, which tells the function how many cluster centers we want to use:
```{r}
iris %>% select(-Species) %>% # remove Species column
  kmeans(centers=3) ->        # do k-means clustering with 3 centers
  km                          # store result as `km`

# now display the results from the analysis
km
```
The cluster means give us the locations of the centroids of the three clusters. We can access them directly via `km$centers`:
```{r}
km$centers
```

The clustering vector tells us for each data point to which cluster it belongs. We can access this vector directly via `km$cluster`:
```{r}
km$cluster
```

We can add this vector to the iris data frame and then plot, coloring by cluster and using different symbol shapes according to species, for comparison:
```{r}
# add species information back into PCA data
# we use `factor(km$cluster)` to tell R that the cluster numbers represent distinct categories,
# not continuous values 
iris_clustered <- data.frame(iris, cluster=factor(km$cluster))
ggplot(iris_clustered, aes(x=Petal.Width, y=Sepal.Width, color=cluster, shape=Species)) + geom_point()
```
Let's do everything once more:
```{r}
iris %>% select(-Species) %>% kmeans(centers=3) -> km
iris_clustered <- data.frame(iris, cluster=factor(km$cluster))
ggplot(iris_clustered, aes(x=Petal.Width, y=Sepal.Width, color=cluster, shape=Species)) + geom_point()
```
*What do you notice? Repeat the clustering and plotting three more times. Do you always get the same result?*
```{r}
# R code goes here.
```

*Look up the meaning of the parameter `nstart` in the documentation to `kmeans()`. Can you use it to make the results more reliable?*

```{r}
# R code goes here.
```

*Now try different numbers of centers and see what you get.*
```{r}
# R code goes here.
```


# 2. Clustering the biopsy data set

*Take the `biopsy` data set, cluster it into 2, 3, or 4 clusters, and display the clusters in principal-component space. (In other words, plot PC2 vs PC1 and color by cluster. You can set the plotting symbol by outcome, to see how clustering compares with known outcomes.)*
```{r}
# load in the biopsy data set
biopsy <- read.csv("http://wilkelab.org/classes/SDS348/data_sets/biopsy.csv")
head(biopsy)
# do PCA on biopsy data set
biopsy %>% select(-outcome) %>% scale() %>% prcomp() -> pca
```


```{r}
# R code goes here.
```

# 3. If this was easy

*Let's go back to the original clustering of the iris data set, with 3 clusters:*
```{r}
iris %>% select(-Species) %>% kmeans(centers=3, nstart=10) -> km
iris_clustered <- data.frame(iris, cluster=factor(km$cluster))
ggplot(iris_clustered, aes(x=Petal.Width, y=Sepal.Width, color=cluster, shape=Species)) + geom_point()
```
*Take this plot and add to it the location of the centroids for each cluster, plotted as large, colored circles with a black outline.*

```{r}
# R code goes here.
```