```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
library(ggplot2)
theme_set(theme_bw(base_size=12))
library(dplyr)
library(tidyr)
```
##In-class worksheet 13
**Mar 3, 2015**


# 1. Working with training and test data sets

We continue working with the biopsy data set:
```{r}
biopsy <- read.csv("http://wilkelab.org/classes/SDS348/data_sets/biopsy.csv")
```

We will need this function from last time, which calculates ROC curves: 
```{r}
calc_ROC <- function(probabilities, known_truth, model.name=NULL)
  {
  outcome <- as.numeric(factor(known_truth))-1
  pos <- sum(outcome) # total known positives
  neg <- sum(1-outcome) # total known negatives
  pos_probs <- outcome*probabilities # probabilities for known positives
  neg_probs <- (1-outcome)*probabilities # probabilities for known negatives
  true_pos <- sapply(probabilities,
                     function(x) sum(pos_probs>=x)/pos) # true pos. rate
  false_pos <- sapply(probabilities,
                     function(x) sum(neg_probs>=x)/neg)
  if (is.null(model.name))
    result <- data.frame(true_pos, false_pos)
  else
    result <- data.frame(true_pos, false_pos, model.name)
  result %>% arrange(false_pos, true_pos)
  }
```

The following code splits the biopsy data set into a random training and test set:
```{r}
train_fraction <- 0.4 # fraction of data for training purposes
set.seed(126)  # set the seed to make your partition reproductible
n_obs <- nrow(biopsy) # number of observations in biopsy data set
train_size <- floor(train_fraction * nrow(biopsy)) # number of observations in training set
train_indices <- sample(1:n_obs, size = train_size)

train_data <- biopsy[train_indices, ] # get training data
test_data <- biopsy[-train_indices, ] # get test data
```

*Fit a logistic regression model on the training data set, then predict the outcome on the test data set, and plot the resulting ROC curves. Limit the x-axis range from 0 to 0.25 to zoom into the ROC curve.*
```{r}
# model to use: 
# outcome ~ clump_thickness + uniform_cell_size + uniform_cell_shape

# R code goes here
```

# 2. Area under the ROC curves

The following code (commented out) calculates the area under multiple ROC curves:
```{r}
#ROCs %>% group_by(model.name) %>% 
#  mutate(delta=false_pos-lag(false_pos)) %>%
#  summarize(AUC=sum(delta*true_pos, na.rm=T)) %>%
#  arrange(desc(AUC))
```

*Use this code to calculate the area under the training and test curve for this following model.*
```{r}
# model to use:
# outcome ~ clump_thickness

train_fraction <- 0.2 # fraction of data for training purposes
set.seed(101)  # set the seed to make your partition reproductible
n_obs <- nrow(biopsy) # number of observations in biopsy data set
train_size <- floor(train_fraction * nrow(biopsy)) # number of observations in training set
train_indices <- sample(1:n_obs, size = train_size)

train_data <- biopsy[train_indices, ] # get training data
test_data <- biopsy[-train_indices, ] # get test data

# Your R code goes here
```

# 3. If this was easy

*Write code that generates an arbitrary number of random subdivisions of the data into training and test sets, fits a given model, calculates the area under the curve for each test data set, and then calculates the average and standard deviation of these values.*
```{r}
# R code goes here
```
