```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
library(ggplot2)
theme_set(theme_bw(base_size=12))
library(dplyr)
```
##In-class worksheet 5
**Feb 3, 2015**

## 1. Tidy data

*Is the `iris` dataset tidy? Explain why or why not.*
```{r}
head(iris)
```
Explanation goes here.

## 2. Selecting rows and columns

*Pick all the rows in the `iris` dataset that pertain to species setosa, and store them in a new table called `iris.setosa`.*
```{r }
# R code goes here.
```

*Pick all the rows in the `iris` dataset where species virginica has a sepal length > 7.*
```{r }
# R code goes here.
```

*Are there any cases in this data set for which the ratio of sepal length to sepal width exceeds the ratio of petal length to petal width? Use `filter()` to find out.*
```{r }
# R code goes here.
```


*Create a pared-down table which contains only data for species setosa and which only has the columns `Sepal.Length` and `Sepal.Width`. Store the result in a table called `iris.pared`.*
```{r }
# R code goes here.
```

## 3. Grouping and summarizing

*Calculate the mean and standard deviation of the sepal lengths for each species.*
```{r }
# R code goes here.
```

*Count the number of observations for each species.*
```{r }
# R code goes here.
```

*For each species, calculate the percentage of cases with sepal length > 5.5.*
```{r }
# R code goes here.
```

## 4. Creating new data, arranging

*Order the data in the `iris` table from largest to smallest sepal length.*
```{r }
# R code goes here.
```

*Create a data column that holds the ratio of sepal length to sepal width. Then order the data by species name and by increasing values of sepal length-to-width ratio. Store the result in a table called `iris.ratio`*
```{r }
# R code goes here.
```


## 5. If this was easy

*Take the `iris.ratio` data set you have created and plot the distribution of sepal length-to-width ratios for the three species.*
```{r }
# R code goes here.
```

*Now plot sepal length-to-width ratios vs. sepal lengths. Does it look like there is a relationship between the length-to-width ratios and the lengths? Does it matter whether you consider each species individually or all together? How could you find out?*
```{r }
# R code goes here.
```
Discussion goes here.