```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
library(ggplot2)
theme_set(theme_bw(base_size=12))
library(dplyr)
library(tidyr)
```
##In-class worksheet 8
**Feb 12, 2015**

## 1. Making wide tables longer
*Consider the following data set, which contains information about income and religious affiliation in the US:*
```{r}
pew <- read.csv("http://wilkelab.org/classes/SDS348/data_sets/pew.csv", stringsAsFactors=F, check.names=F)
head(pew)
```
*This table is not tidy, because income levels are used as column headers rather than as levels of an `income` variable. Use `gather()` to turn this table into a table with three columns, one for religion, one for income (called `income`), and one for the count of people with the respective combination of income and religion (called `count`).*
```{r}
# R code goes here.
```

*Now call the income column `income_level` and the count column `number_of_people`.*
```{r}
# R code goes here.
```

*Now, instead of gathering data from all columns, gather only the data from columns `below10k`, `from20to30k`, and `from50to75k`, such that your final dataframe contains only these three income levels. Sort your final data frame according to religion, using income_level to break any ties.*
```{r}
# R code goes here.
```

## 2. Making long tables wider
*Consider the following data set, which contains information about the sex, weight, and height of 200 individuals:*
```{r}
persons <- read.csv("http://wilkelab.org/classes/SDS348/data_sets/persons.csv", stringsAsFactors=F)
head(persons)
```
*Is this data set tidy? And can you rearrange it so you have a column for subject, one for sex, one for weight, and one for height?*

Explanation goes here.
```{r}
# R code goes here.
```

*For the data set `diamonds` from the ggplot2 package, create a table displaying the mean price for each combination of cut and clarity. Then use `spread()` to rearrange this table into a wide format, such that there is a column of mean prices for each cut level (Fair, Good, Very Good, etc.).*

```{r}
# R code goes here.
```


## 3. If this was easy

*Consider the following code and its output. Can you explain why the result looks the way it does? Do you have any idea how to avoid the NAs?*

```{r}
iris %>% select(Sepal.Length, Species) %>% spread(Species, Sepal.Length)
```
Explanation goes here.