```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
library(ggplot2)
theme_set(theme_bw(base_size=12))
library(dplyr)
```
##In-class worksheet 7
**Feb 10, 2015**

## 1. Relationship between arrival delay and age of plane

*The nycflights13 data contains information about all planes departing fron New York City in 2013. The table `flights` contains information about individual departures:*
```{r}
library(nycflights13)
flights
```
*Individual planes are indicated by their tail number (`tailnum` in the table). Calculate the mean arrival delay (`arr_delay`) for each tail number.*
```{r}
# R code goes here.
```
*Information about individual planes is availabe in the table `planes`:*
```{r}
planes
```
*In particular, this table lists the year each individual plane was manufactured. Make a combined table that holds tail number, mean arrival delay, and year of manufacture for each plane. Then plot mean arrival delay vs. year of manufacture.*
```{r}
# R code goes here.
```

## 2. Relationship between arrival delay and temperature
*Now calculate the mean arrival delay for each day of the year. Note: you need to use `mean(arr_delay, na.rm=T)` to get meaningful results. The `na.rm=T` removes missing values before averaging. Without this line, almost all averaged end up as missing values (`NA`).*
```{r}
# R code goes here.
```

*We want to correlate these delay values with the temperature of each day. The data frame `weather` holds temperature measurements for each hour of each day:*
```{r}
weather
```
*First, calculate the mean temperature for each day:*
```{r}
# R code goes here.
```
*Now combine the mean delay and the mean temperature into one table, and then plot mean delay vs. mean temperature.*
```{r}
# R code goes here.
```

## 3. If this was easy

*Find out for how many tail numbers in the `flights` data set we have no information in the `planes` data set. What do we have to pay attention to when joining the `flights` and `planes` tables?*
```{r}
# R code goes here.
```

*Calculate the mean arrival delay by plane model or plane engine. Sort in order of descending mean delay. Remove all tailnumbers for which no plane information is available.*
```{r}
# R code goes here.
```

