```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
```
## In-class worksheet 6
**Feb 7, 2019**

In this worksheet, we will continue to work with the tidyverse libraries:
```{r message=FALSE}
library(tidyverse)
```

## 1. The msleep dataset

The `msleep` dataset, provided with ggplot2, contains information about sleep and awake times of different mammals:
```{r}
msleep
```

Verify that the sum of total sleep time (column `sleep_total`) and total awake time (column `awake`)  adds up to 24h for all animals in the `msleep` dataset.
```{r}
# R code goes here.
```

Make a list of all the domesticated species in the `msleep` dataset, in alphabetical order. Hint: Domesticated species have the entry "domesticated" in the column `conservation`.
```{r}
# R code goes here.
```

For the different vore classifications, tally how many species are awake for at least 18 hours. Hint: Use the function `tally()`.
```{r}
# R code goes here.
```

Using the function `top_n()`, identify the top-10 least-awake animals and list them from least awake to most awake. Explain why this analysis gives you 11 results instead of 10. Hint: Before calling `top_n()`, use the function `select()` to extract the two columns `name` and `sleep_total`, in that order.
```{r}
# R code goes here.
```

Considering only carnivores and herbivores, make a plot of the percent of time each animal is in REM sleep (out of the total sleep time) vs. the animal's total sleep time. Hint: Use the operator `|` to indicate logical OR in the `filter()` function.
```{r}
# R code goes here.
```


## 2. The diamonds dataset

The `diamonds` dataset provided by ggplot2 provides information about quality and price of 53940 diamonds:
```{r}
head(diamonds)
```

The best cuts of diamonds are "Very Good", "Premium", and "Ideal". Make a table that selects only those diamonds, and find the minimum, median, and maximum price for each cut. Hint: The operator `%in%` is helpful for selecting the diamond cuts.
```{r}
# R code goes here.
```

For each of the different diamond cuts, calculate the mean carat level among the diamonds whose price falls within 10% of the most expensive diamond for that cut.
```{r}
# R code goes here.
```

For each of the different diamond cuts, calculate the mean carat level among the top-10% most expensive diamonds.
```{r}
# R code goes here.
```

Make a table that contains the median price for each combination of `cut` and `clarity`, and arrange the final table in descending order of median price.
```{r}
# R code goes here.
```

Now arrange the same table first by cut and then within each cut group by median price.
```{r}
# R code goes here.
```


## 3. If this was easy

For the `diamonds` data set, separately for each diamond cut, calculate the percentage of diamonds with a price above \$10,000, and the median carat value for diamonds priced \$10,000 or more.
```{r}
# R code goes here.
```
