```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
library(ggplot2)
theme_set(theme_bw(base_size=12))
library(dplyr)
library(tidyr)
```
##Homework 4
*Enter your name and EID here*

**This homework is due on Feb. 14, 2017 at 7:00pm. Please submit as a PDF file on Canvas.**

**Problem 1: (4 pts)** Recall the `HairEyeColor` data set from an earlier in-class exercise. This data set contains counts of males and females with different combinations of hair and eye color.

```{r}
HairEyeColor
```

I have split the data set into two data-frames, one `male` and one `female`. Using the `dplyr` and `tidyr` packages, make these data-frames tidy and then combine them into a single data-frame. Make sure that your final data-frame has a `sex` column indicating which data-frame the observations originally came from. **HINT**: You can use the `bind_rows` function to add rows from one data-frame onto another as long as both data-frames have identical column names.

```{r}
male <- read.table(text="
Hair    Brown Blue Hazel Green
  Black    32   11    10     3
  Brown    53   50    25    15
  Red      10   10     7     7
  Blond     3   30     5     8
", head=T)

female <- read.table(text="
Hair    Brown Blue Hazel Green
  Black    36    9     5     2
  Brown    66   34    29    14
  Red      16    7     7     7
  Blond     4   64     5     8
", head=T)

# R code goes here
```

Using the data-frame you created above, compute the total counts for each sex (i.e., the sum of the counts for each sex).

```{r}
# R code goes here
```

**Problem 2: (3 pts)** Recall that the `chickwts` data set contains information on the weight of chicks after being fed different feed supplements. The different feed supplements are labeled casein, horsebean, linseed, meatmeal, soybean, and sunflower in the `feed` column. I have created a new data-frame (`feed_names`), that contains the abbreviated names of different feed supplements. Using one of the `dplyr` join functions, combine the two data-frames so that there is an additional `feed_abbr` column and all of the original columns and rows in `chickwts` are retained. Which join function is most appropriate to use and why?

```{r}
head(chickwts)

feed_names <- read.table(text="
feed feed_abbr
casein cs
whey wh
linseed  ls
meatmeal mm
fishmeal fm
soybean sb
sunflower sf
corn co
wheatbran wb
", head=T)

# R code goes here
```

*Your answer goes here. 1-2 sentences only.*

**Problem 3: (3 pts)** Make up your own data set which is **not** tidy and input it into R via the `text` option of `read.table()`. First, explain why it is not tidy. Then, using `dplyr` and/or `tidyr` convert it into a tidy data set.

```{r}
# R code goes here
```

*Your answer goes here*

```{r}
# R code goes here
```
