```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=4, fig.width=6)
library(ggplot2)
theme_set(theme_bw(base_size=12))
library(dplyr)
```
##Homework 5
*Enter your name and EID here*

**This homework is due on Feb. 28, 2017 at 7:00pm. Please submit as a PDF file on Canvas.**

*For this homework you will use the `mrna` data set. The `mrna` data set contains gene expression of E.coli grown on minimal medium for two weeks. There are three replicates for each time course. Each row represents observations for different samples. The first five columns correspond to sample name (`dataSet`), carbon source (`carbonSource`), growth time in hours (`growthTime_hr`), bacterial growth phase (`growthPhase`), and batch number (`batchNumber`). The batch number indicates samples that were grown as part of the same replicate. The rest of the columns correspond to gene expression for each gene. The gene names start with ECB (i.e. `ECB_00001`).*

```{r}
mrna <- read.csv("http://wilkelab.org/classes/SDS348/data_sets/AG3C_mrna_counts.csv")
mrna <- as_data_frame(mrna) #convert to tibble for easier visualization
mrna
```

**Problem 1 (3 pts):** *Perform a principal components analysis (PCA) on gene expression. You do not need to **scale** the data before running PCA because gene expression in this data set have already been normalized. Create a scatterplot of PC1 vs. PC2. First, color each point by bacterial growth phase, and then color each point by batch number. What do you observe? Visually, and without doing any calculations, do the growth phases cluster together in principal-component space? Do the batch numbers cluster together?*

```{r}
# your R code goes here
```

*Your answer goes here. 1-2 sentences only.*

**Problem 2 (4 pts):** *Now take your matrix of **principal components coordinates** (not the raw gene expression values!) from Question 1 above and cluster the gene expression into 3 groups (`centers=3`) using k-means clustering with 10 random starts (`nstart=10`). Create a scatterplot of PC1 vs. PC2. This time, color each point by **cluster** and set the plotting symbol by **growth phase**. What do you observe?*

```{r}
# your R code goes here
```

*Your answer goes here. 1-2 sentences only.*

**Problem 3 (3 pts):** *Create a bar plot that shows the percent variance explained by the first 10 principal components. State how much variance is explained by each of the principal components 1 through 4.*

```{r}
# your R code goes here
```

*Your answer goes here. 1-2 sentences only.*
