```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
```
##In-class worksheet 6
**Feb 4, 2016**

In this worksheet, we will use the libraries ggplot2 and dplyr:
```{r message=FALSE}
library(ggplot2)
library(dplyr)
```

## 1. The msleep dataset

The `msleep` dataset, provided with ggplot2, contains information about sleep and awake times of different mammals:
```{r}
msleep
```

Verify that the sum of total sleep time (column `sleep_total`) and total awake time (column `awake`)  adds up to 24h for all animals in the `msleep` dataset.
```{r}
# R code goes here.
```

Make a list of all the domesticated species in the `msleep` dataset, in alphabetical order. Hint: domesticated species have the entry "domesticated" in the column `conservation`.
```{r}
# R code goes here.
```

For the different vore classifications, tally how many species are awake for at least 18 hours. Hint: use the function `tally()`.
```{r}
# R code goes here.
```

Using the function `top_n()`, identify the top-10 least-awake animals, and list them from least awake to most awake. Explain why this analysis gives you 11 results instead of 10.
```{r}
# R code goes here.
```

Considering only carnivores and herbivores, make a plot of the percent of time each animal is in REM sleep (out of the total sleep time) vs. the animal's total sleep time. Hint: Use the operator `|` to indicate logical OR in the `filter()` function.
```{r}
# R code goes here.
```


## 2. The diamonds dataset

The `diamonds` dataset provided by ggplot2 provides information about quality and price of 53940 diamonds:
```{r}
head(diamonds)
```

The best cuts of diamonds are "Very Good", "Premium", and "Ideal". Make a table that selects only those diamonds, and find the minimum, median, and maximum price for each cut. Hint: The operator `%in%` is helpful for selecting the diamond cuts.
```{r}
# R code goes here.
```

For each of the different diamond cuts, calculate the mean carat level among the diamonds whose price falls within 10% of the most expensive diamond for that cut.
```{r}
# R code goes here.
```

For each of the different diamond cuts, calculate the mean carat level among the top-10% most expensive diamonds.
```{r}
# R code goes here.
```

Make a table that contains the median price for each combination of `cut` and `clarity`, and arrange the final table in descending order of median price. Do you notice something odd about the ordering?
```{r}
# R code goes here.
```


## 3. If this was easy

For the `diamonds` data set, using the function `do()`, fit a linear model of price vs. carat separately for each cut. Then make a table that holds the resulting intercepts and slopes.
```{r}
# R code goes here.
```
