```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=3, fig.width=4)
```
##In-class worksheet 5
**Feb 2, 2016**

## 1. Tidy data

Is the `iris` dataset tidy? Explain why or why not.
```{r}
head(iris)
```
*Your answer goes here.*

Is the `HairEyeColor` dataset tidy? Explain why or why not.
```{r}
HairEyeColor
```
*Your answer goes here.*

## 2. Selecting rows and columns
All subsequent code will be based on the dplyr library. So we first have to load this library:
```{r message=FALSE}
library(dplyr)
```

Now, using the dplyr function `filter()`, pick all the rows in the `iris` dataset that pertain to species setosa, and store them in a new table called `iris.setosa`.
```{r }
# R code goes here.
```

Pick all the rows in the `iris` dataset where species virginica has a sepal length > 7.
```{r }
# R code goes here.
```

Are there any cases in the `iris` dataset for which the ratio of sepal length to sepal width exceeds the ratio of petal length to petal width? Use `filter()` to find out.
```{r }
# R code goes here.
```


Create a pared-down table which contains only data for species setosa and which only has the columns `Sepal.Length` and `Sepal.Width`. Store the result in a table called `iris.pared`.
```{r }
# R code goes here.
```

## 3. Creating new data, arranging

Using the function `mutate()`, create a new data column that holds the ratio of sepal length to sepal width. Store the resulting table in a variable called `iris.ratio`.
```{r }
# R code goes here.
```

Order the `iris.ratio` table by species name and by increasing values of sepal length-to-width ratio.
```{r}
# R code goes here.
```

## 4. Grouping and summarizing

Calculate the mean and standard deviation of the sepal lengths for each species. Do this by first creating a table grouped by species, which you call `iris.grouped`. Then run `summarize()` on that table.
```{r }
# R code goes here.
```

Use the function `n()` to count the number of observations for each species.
```{r }
# R code goes here.
```

For each species, calculate the percentage of cases with sepal length > 5.5.
```{r }
# R code goes here.
```


## 5. If this was easy

Take the `iris.ratio` data set you have created and plot the distribution of sepal length-to-width ratios for the three species.
```{r }
# R code goes here.
```

Now plot sepal length-to-width ratios vs. sepal lengths. Does it look like there is a relationship between the length-to-width ratios and the lengths? Does it matter whether you consider each species individually or all together? How could you find out?
```{r }
# R code goes here.
```
