```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=4, fig.width=4)
```
##In-class worksheet 1

**Jan 19, 2016**


Much of the work in this class will be done via R Markdown documents. R Markdown documents are documents that combine text, R code, and R output, including figures. They are a great way to produce self-contained and documented statistical analyses.

In this first worksheet, you will learn how to do some basic markdown editing. After you have made a change to the document, press "Knit HTML" in R Studio and see what kind of a result you get.

Edit only below this line.

---------------------------------------------
## 1. Basic Markdown editing
Try out basic R Markdown features, as described [here.](http://rmarkdown.rstudio.com/authoring_basics.html) Write some text that is bold, and some that is in italics. Make a numbered list and a bulleted list. Make a nested list. Try the block-quote feature.

## 2. Embedding R code

R code embedded in R chunks will be executed and the output will be shown.
```{r}
# R code goes here
x <- 5
y <- 7
z <- x * y
z
```

Play around with some basic R code. E.g., take the built-in data set `cars`, which lists speed and stopping distance for cars from the 1920. Plot speed vs. distance, and/or perform a correlation analysis. Then write a few sentences describing what you see.

## 3. If this was easy

If this was easy, use Google to find out how to type-set mathematical formulas inside of R markdown.




